
%\newpage
\chapter{To Do List and new ideas}
\label{sec:todo}

\begin{enumerate}
\item Add more and better documentation.
\item Think about how we can get the real internal resistance of port B output (resistor switching port) instead of assuming, that ports are equal.
\item Can discharging of capacitors be made more quickly, if the minus pin is additionally raised
with the \(680\Omega\) resistor to VCC (+)?
\item Check if the tester can use floating-point representation of  values. The risk of overflow  is lower.
There is no need to use multiplication and division together to build a multiplication with a non integer factor.
But I don't know how much flash memory must be spend for the library.
\item Write User's guide for configuring the tester with the Makefile options and description of the build chain.
\item If the holding current of a thyristor can not be reached with the \(680\Omega\) resistor, is it harmless to switch the cathode directly to GND
and the anode directly to VCC for a very short time?
The current could reach more than 100mA. Will the port be damaged? What is with the power supply (voltage regulator)?
\item Check the Port afterwards with self test function!
\item Warning message, if the found reference voltage is not plausible in relation to ATmega model and VCC.
\item What is about a second generation tester with a bigger ATmega which includes differential ADC-port, more flash memory …. ?
There is no ATxmega which have supply voltage of 5V, only the ATmega line  is possible. 
\item Idea for a New Projekt: USB  version without LCD-Display, Power from USB, Communication to PC over a USB-Serial bridge.
\end{enumerate}
